Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-25 snapshot_system/failover.tex
replace the data sharing grpah

\subsection{Fault Analysis }

@@

To  compute the probablity of losing a virtual machine, 
we estimate the number of file system blocks per VM in each apporach.
We can build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
if this file is used by this VM. 
For VC, let $N_1$ be the averge number of file system blocks for non-CDS data for each VM
and  $N_2$ be the averge number of file system blocks for CDS data for each VM.
For VO, let $N_o$ be the averge number of file system blocks for each VM
and  let $V_o$ be the averge number of VMs shared by each file system block.
Figure~\ref{fig:shared} illustates the bipartite association.
\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{shared.pdf}
\caption{Assoication of data blocks to VMs.}
\label{fig:shared}
\end{figure}

>>>>

\subsection{Fault Analysis }
\begin{figure}
    \centering
    \subfigure[Sharing of data under VM-oblivious dedup model]
    {
        \includegraphics[width=3in]{images/share_model_vc.pdf}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of data under VM-centric dedup model]
    {
        \includegraphics[width=3in]{images/share_model_vo.pdf}
        \label{fig:share_vo}
    }
    \caption{Difference of sharing data under VO and VC approaches}
    \label{fig:share}
\end{figure}

@@

To  compute the probablity of losing a virtual machine, 
we estimate the number of file system blocks per VM in each apporach.
We can build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
if this file is used by this VM. 
For VC, let $N_1$ be the averge number of file system blocks for non-CDS data for each VM
and  $N_2$ be the averge number of file system blocks for CDS data for each VM.
For VO, let $N_o$ be the averge number of file system blocks for each VM
and  let $V_o$ be the averge number of VMs shared by each file system block.
Figure~\ref{fig:shared} illustates the bipartite association.
